Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-18 cordillera-cycle.tex
Add acknowledgements.

% Acknowledgements
%\begin{acknowledgements}
  % Author contributions
  %\hack{\noindent}\textit{Author contributions.}
%\end{acknowledgements}

>>>>

% Author contributions
\section*{Author contributions}
\dots

% Acknowledgements
\begin{acknowledgements}
We are very thankful to Constantine Khroulev, Ed Bueler and Andy Aschwanden for
providing constant help and development on PISM. This work was supported by the
Swedish Research Council~(VR) grant no. 2008-3449 to A.~P.~Stroeven, by the
German Academic Exchange Service~(DAAD) grant no.~50015537 and a Knut and Alice
Wallenberg Foundation grant to J.~Seguinot, and by NASA grant no.~NNX13AM16G
to E.~Bueler. Computer resources were provided by the Swedish National
Infrastructure for Computing (SNIC) allocation no. 2013/1-159 to A.~P.~Stroeven
at the National Supercomputing Center (NSC).
\end{acknowledgements}
